---
title: "Introduction to devtri"
author: "Andy Merlino"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `devtri` package, short for **dev**elopment **tri**angle, makes it easy to work with actuarial loss development triangles.

### Step 1: Load the pakage look at the data

We will be working with the `tri_data` data set which comes from the `devtri` package.  This data is just an ordinary data frame with 3 columns.

```{r load_data, message=FALSE}
library(devtri)

head(tri_data, 10)
```

### Step 2

Turn the above data frame into a triangle object

```{r}
my_tri <- dev_tri(
   origin = tri_data$origin,
   age = tri_data$dev,
   value = tri_data$paid)

my_tri
```

This object now includes class `tidy_tri`.

```{r}
class(my_tri)
```

As you have probably noticed, this object does not look like a triangle.  It is still in tidy/long form where each row represents one observation.  Keeping the data in a tidy form makes it much easier to work with. If you want to create an actual triange, run: 

```{r}
spread_tri(my_tri)
```

Trinagles in the form shown above will not be used in any of the development functions, but they are conventiant for viewing and presenting.

### Step 3

Calculate the agte-to-age development factors and select the development factors we will use in our reserve estimation.

```{r}
my_ata <- ata_tri(my_tri)

my_ata
```

```{r}
spread_tri(my_ata)
```

Here we are just going to use the straight average for the ldfs.

```{r }
my_ldf <- ldf_avg(my_tri)
my_ldf
```

Convert to cdf

```{r}
my_cdf <- idf2cdf(my_ldf)
my_cdf
```

### Step 4

Get latest losses

```{r}
my_latest <- latest(my_tri)

my_latest
```

### Step 5

Run development projection

```{r}
est <- left_join(my_latest, my_cdf[, -3], by = "age")

est <- est %>%
         mutate(est_ult = value * ldf)
est
```

You can use a dollar weighted average instead of a straight average: 

```{r}
my_wtd <- ldf_avg_wtd(my_tri)
my_wtd
```

### Interpolation

linearly interpolate our cdf 0.25 periods into the future:

```{r}
interpolate_linear(my_cdf, dev = 0.25)
```

You can see above that the final value in the `ldf` column is equal to 1.0.  This `ldf` value is set to 1.0 because no tail factor method is set for the `idf` object.  To set a tail for the `idf` object, you pass it to a `tail_*()` function:

```{r}
my_ldf_w_tail <- idf(
                   ldfs = c(1.25, 1.05, 1.04),
                   first_age = 1) %>%
                   tail_linear()

my_ldf_w_tail
attr(my_ldf_w_tail, "tail")
```
